---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

#Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

``` {r load_libraries, message=F, warning=F}
library(nlme)
library(xtable)
library(lme4)
library(readr)
library(ggplot2)
library(lsmeans)
library(car)
```


```{r import_data}

# Import data
df <- read_csv("~/Google Drive/skinner/Pecina_k/alex_behav_full_merge_with_PEbetas.csv")

# recode, rename ROIs
# df <- read_csv("~/Google Drive/skinner/Pecina_k/alex_behav_full_merge_with_betas.csv")
df$Sex <- as.factor(df$Sex)
df$subject<- as.factor(df$subject)
# rename ROIs
df$new_L_postcentr_1 <-  df$PEmag_left_postcentral
df$new_visual_2 <- df$PEmag_visual
df$new_acc_3 <- df$PEmag_ant_cingulate
df$new_R_postcentr_4 <- df$PEmag_right_postcentral
df$new_striatum_5 <- df$PEmag_ventral_striatum
df$new_cereb1_6 <- df$PEmag_right_cullmen
df$new_cereb2_7 <- df$PEmag_cerebellum

# make the trial-level dataframe
df <- subset(df, select=c(1:3,20:23,4:19,24:167))

# and a subject-level dataframe
library(reshape2)
attach(df)
aggdata <-aggregate(df, by=list(subject), 
  FUN=mean, na.rm=TRUE)
print(aggdata)
detach(df)
#View(aggdata)
sdf <- aggdata
```

```{r ROI correlation matrix }
ROIcor <- cor(sdf[162:168], use = "complete.obs")


library(corrplot)

# corrplot(ROIcor, order="hclust", method="circle", tl.pos="n",  type = "upper",       
# tl.col="black", tl.cex=2.0, tl.srt=45, 
#          addCoef.col="black", addCoefasPercent = FALSE,
#          p.mat = 1-abs(ROIcor), sig.level=0.7, insig = "blank")  

corrplot(ROIcor,type = "upper", tl.pos = "td", cl.lim=c(0,1),
         method = "circle", tl.cex = 1, tl.col = 'black',
         order = "hclust", diag = FALSE, 
         addCoef.col="black", addCoefasPercent = FALSE,
        p.mat = 1-abs(ROIcor), sig.level=0.7, insig = "blank")

```
```{r ROI PCA}
roipca <- prcomp(na.omit(sdf[162:168]), center = TRUE, scale = TRUE)
print(roipca)
summary(roipca)

plot(roipca, type = "l")
# <!-- install_github("ggbiplot", "vqv") -->
# 
# <!-- library(ggbiplot) -->
# <!-- g <- ggbiplot(roipca, obs.scale = 1, var.scale = 1,  -->
# <!--               groups = df$subject, ellipse = TRUE,  -->
# <!--               circle = TRUE) -->
# <!-- g <- g + scale_color_discrete(name = '') -->
# <!-- g <- g + theme(legend.direction = 'horizontal',  -->
# <!--                legend.position = 'top') -->
# <!-- print(g) -->
```


``` {r behavioral model of feedback ratings}
# nm1 <- (lmer(feedback_rating ~ stim_rating + feedback + feedback_ratinglag + (1 +feedback + stim_rating |subject), df))
# summary(nm1)
# car::Anova(nm1)

 # basic model
nm2 <- (lmer(feedback_rating ~ stim_rating*stim + feedback + feedback_ratinglag + (1 +feedback + stim_rating |subject), df))
summary(nm2)
car::Anova(nm2)
# anova(nm1,nm2)

ls_nm2 <- lsmeans(nm2,"stim_rating",by = "stim", at = list(stim_rating = c(-2,-1,0,1,2)))
plot(ls_nm2, type ~ stim_rating, horiz=F, ylab = "Mood ratings", xlab = "Expectancy")

```

``` {r neural model of feedback ratings}
nm3 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + new_visual_2*stim + (1 +feedback + stim_rating |subject), df))
summary(nm3)
car::Anova(nm3)

nm4 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + new_L_postcentr_1*stim + (1 +feedback + stim_rating |subject), df))
summary(nm4)
car::Anova(nm4)
anova(nm3,nm4)
# above model did not converge, to be investigated


nm5 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + new_striatum_5*stim + (1 +feedback + stim_rating |subject), df))
summary(nm5)
car::Anova(nm5)
anova(nm3,nm5)

ls_nm5 <- lsmeans(nm5,"stim",by = "new_striatum_5", at = list(new_striatum_5 = c(1,5,10)))
setwd("/Users/localadmin/Google Drive/skinner/Pecina_k/results/")
# pdf("str_modulation.pdf", width=5, height=3.5)
plot(ls_nm5, type ~ stim, horiz=F, ylab = "Mood ratings", xlab = "infusion", main = "Striatal activity modulates effect of infusion on mood ratings")

# can we replicate this with an unbiased striatal ROI?
nm5 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + df$new_striatum_5*stim + (1 +feedback + stim_rating |subject), df))
summary(nm5)
car::Anova(nm5)

``` 

``` {r behavioral model of infusion ratings}
## em stands for expectancy model - same as nm, but run on infusion ratings

em1<- (lmer(stim_rating ~ stim + feedback_ratinglag  + (1 +stim  |subject), df))
summary(em1)
car::Anova(em1)

```

``` {r neural model of infusion ratings}

em2<- (lmer(stim_rating ~ stim + feedback_ratinglag*new_striatum_5 + stim_diff  + (1 +stim  |subject), df))
summary(em2)
car::Anova(em2)

ls_em2 <- lsmeans(em2,"feedback_ratinglag",by = "new_striatum_5", at = list(new_striatum_5 = c(1,5,10),feedback_ratinglag = c(-2,0,2)))
# pdf("str_modulation_feedback_rating_lag.pdf", width=5, height=3.5)
plot(ls_em2, type ~ stim, horiz=F, ylab = "Expectancy ratings", xlab = "Previous mood ratings", main = "Striatal activity enhances the effect of previously reported mood")
# dev.off()

```
``` {r models of individual differences in feedback ratings: demographics}
# include indiv. differences in feedback rating models
# df$apathy <- scale(df$ApathyEvaluationScale)


# im stands for "individual differences model"
# first rerun the behavioral model
im1 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + (1 +feedback + stim_rating |subject), df))
summary(im1)
car::Anova(im1)


im2 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + YearsOfEd*feedback*stim + (1 +feedback + stim_rating |subject), df, na.action = na.omit))
summary(im2)
car::Anova(im2)

ls_im2 <- lsmeans(im2, "stim", by ="YearsOfEd", at = list(YearsOfEd = c(8,13,18)),data = df)
plot(ls_im2, type ~ stim, horiz=F, by = "YearsOfEd",  ylab = "Mood ratings", xlab = "Infusion")

#im3 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + Sex*feedback + (1 +feedback + stim_rating |subject), df, na.action = na.omit))
#summary(im3)
#car::Anova(im3)

#ls_im3 <- lsmeans(im3, "feedback", by ="Sex",at = list(feedback = c(-2,-1,1,2)),data = df)
#plot(ls_im3, type ~ feedback, horiz=F, by = "Sex",  ylab = "Mood ratings", xlab = "Neurofeedback")


```

``` {r models of individual differences: apathy}

im2 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + df$DAS7*feedback + (1 +feedback + stim_rating |subject), df,na.action = na.omit))
summary(im2)
car::Anova(im2)

```


``` {r models of individual differences: endorphins -- to be completed}
#take a log ratio of post/pre 
df$endorphine_change <- log(df$endorf2/df$endorf1)
hist(df$endorf2_1)
hist(df$endorphine_change)

# effects on feedback
im4 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + endorf1*feedback + (1 +feedback + stim_rating |subject), df))
summary(im4)
car::Anova(im4)

im5 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + endorf2*feedback + (1 +feedback + stim_rating |subject), df))
summary(im5)
car::Anova(im5)

im6 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + endorphine_change*feedback*stim + (1 +feedback + stim_rating |subject), df))
summary(im6)
car::Anova(im6)

im7 <- (lmer(feedback_rating ~ stim_rating*stim + feedback +feedback_ratinglag + endorphine_change*feedback + (1 +feedback + stim_rating |subject), df))
summary(im7)
car::Anova(im7)
anova(im4,im5,im6,im7)

ls_im7 <- lsmeans(im7,"feedback",by = "endorphine_change", at = list(endorphine_change = c(-4,0,4),feedback = c(-2,0,2)))
# pdf("str_modulation_feedback_rating_lag.pdf", width=5, height=3.5)
plot(ls_im7, type ~ feedback, horiz=F, ylab = "Reported mood change", xlab = "Previous mood ratings", main = "Increase in endorphin levels enhances the effect of neurofeedback")

```

<!-- ``` {r check_apathy} -->
<!-- ggplot(data = df, mapping = aes(df$ApathyEvaluationScale,df$subject)) +geom_point(mapping = aes(df$ApathyEvaluationScale,df$subject)) -->

<!-- ggplot(data = df, mapping = aes(df$ApathyEvaluationScale,df$Age)) +geom_point(mapping = aes(df$ApathyEvaluationScale,df$Age)) -->
<!-- ``` -->


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
